Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-19 Manuscript/manuscript.Rmd
manuscript edits

In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several external or data level solutions. These mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset. Many such solutions have been developed in a variety of fields related to machine learning [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical]. Likewise, it has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis,].

>>>>

In addition to employing suitable metrics for evaluating models validated on imbalanced data, there also exist several algorithmic or data level solutions. Algorithmic level solutions involve modifyng existing classifiers in order to curtail the bias induced by imbalanced classes. Many such solutions have been developed in a variety of fields related to machine learning [@estabrooks2004multiple; @chawla2003smoteboost; @chen2004using; @khoshgoftaar2007empirical]. Data level solutions mostly constitute as resampling techniques, in which random sampling is used to either replicate or removed data points in order to create a more balanced dataset.  It has been shown that quite simple resampling techniques can drastically improve model performance in the face of imbalanced data [@japkowicz2002class; @dubey2014analysis,]. For the purposes of this study we focus our attention toward data level solutions so that all results may be classifier independent, and thus, more easily comparable.
